A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2017-06-06 intro.tex
tweak doc

In previous studies, e.g. the Representative Concentration Pathways (RCPs), IAM
results have been harmonized by sector and the 5 RCP global regions
\cite{vuuren_representative_2011}. Climate modeling efforts have continued to
progress, however, demanding increased spatial and sectoral resolution. In order
to address the growing dimensionality of model outputs while still providing a
consistent and scientifically rigorous harmonization procedure, an automated
process for determining harmonization methods is needed. The remainder of this
paper describes the methodology of the \code{aneris} code base
\cite{matthew_gidden_2017_802832}, written in the Python programming language,
which implements such a system in Section \ref{sec:meths} (documentation
available \href{http://mattgidden.com/aneris/}{online}). The results of applying
the automated harmonization mechanism on two example IAM scenarios, one with
emissions growth and another with emissions mitigation, is presented in Section
\ref{sec:results}. Finally, the general effectiveness and potential future
improvements on the automated methodology is discussed in Section
\ref{sec:future}.

>>>>

In previous studies, e.g. the Representative Concentration Pathways (RCPs), IAM
results have been harmonized by sector and the 5 RCP global regions
\cite{vuuren_representative_2011}. Climate modeling efforts have continued to
progress, however, demanding increased spatial and sectoral resolution. In order
to address the growing dimensionality of model outputs while still providing a
consistent and scientifically rigorous harmonization procedure, an automated
process for determining harmonization methods is needed. The remainder of this
paper describes the methodology of the \code{aneris} code base
\cite{matthew_gidden_2017_802832}, written in the Python programming language
(detailed documentation available \href{http://mattgidden.com/aneris/}{online}),
which implements such a system in Section \ref{sec:meths}. The results of
applying the automated harmonization mechanism on two example IAM scenarios, one
with emissions growth and another with emissions mitigation, is presented in
Section \ref{sec:results}. Finally, the general effectiveness and potential
future improvements on the automated methodology is discussed in Section
\ref{sec:future}.
